% Appendix Template

\chapter{User study questionnaire} % Main appendix title

\label{AppendixD} % Change X to a consecutive letter; for referencing this appendix elsewhere, use \ref{AppendixX}

\lhead{Appendix D. \emph{User study questionnaire}} % Change X to a consecutive letter; this is for the header on each page - perhaps a shortened title

A questionnaire is used (English/Japanese) for the user data collection.  
\section*{Questionnaire/アンケート}


\begin{Form}
%\hrule
\section*{Usability/使いやすさについて}
\radioquestion{1}{Was the interface easy to use?}{このインターフェースは使いやすかったですか？}{Very easy}{Very difficult}{簡単だった}{難しかった}

\radioquestion{2}{Do you think tablet application is convenient?}{今回のタブレットアプリケーションは便利でしたか？}{Very easy}{Very difficult}{とてもそう思う}{そうは思わない}

\radioquestion{3}{How long did it take to learn to use the application?}{このアプリケーションに慣れるのにどのくらいかかりましたか？}{Very easy}{Very difficult}{すぐに慣れた}{とても時間がかかった}

\radioquestion{4}{Was the program structure easy to understand?}{プログラムの構成は分かりやすいものでしたか？}{Very easy}{Very difficult}{簡単だった}{難しかった}

\radioquestion{5}{Were the functionality of programming blocks easy to understand?}{プログラムブロックは分かりやすいものでしたか？}{Very easy}{Very difficult}{簡単だった}{難しかった}

\radioquestion{6}{Were you able to create the scenario you wanted to?}{思い通りのシナリオを作ることができましたか？}{Very easy}{Very difficult}{問題なく作ることができた}{全然作れなかった}

\section*{Execution/シナリオの実行について}
\radioquestion{7}{Was the scenario executed as you expected?}{思い通りにシナリオを実行することができましたか？}{Very easy}{Very difficult}{思い通りにできた}{全然違うものだった}

\radioquestion{8}{Did the robot understand your gestures and commands as expected?}{ロボットがあなたのことを理解しているように感じましたか？}{Very easy}{Very difficult}{きちんと理解してくれた}{全然理解してくれなかった}

\radioquestion{9}{Was the robot reactive to your commands and gestures?}{ロボットはあなたの行動に対して適切に反応していましたか？}{Very easy}{Very difficult}{きちんと反応してくれた}{全然反応してくれなかった}

\vspace{.05in}
%\hrule 
\begin{tabular}{rl}
\textbf{10} & \textbf{If the execution has failed, what were the reasons for it?}\\
{} & (You can choose more than one option for this question)\\
{} & \textbf{シナリオの実行がうまくいかなかったとき、その理由が分かりましたか？}\\
{} & (複数回答可))\\
\end{tabular}

\begin{tabular}{rl}
\quad $\square$ & System Failure / システムに原因があった \\
\quad $\square$ & Logical error in the program / プログラムにエラーがあった \\
\quad $\square$ & Robot failed to execute the task as expected / ロボットに原因があった \\
\quad $\square$ & Other / その他 \\
\end{tabular}
\vspace{.1in}

\section*{System/全体のシステムについて}
\vspace{.05in}
%\hrule 
\begin{tabular}{rl}
\textbf{11} & \textbf{How long did it take to design the program and execute in the robot together?}\\
{} & \textbf{プログラムを作り始めてから実行するまでにどのくらい時間がかかりましたか？}\\
\end{tabular}

\begin{tabular}{rl}
\quad $\square$ & Less than 30 minutes / 30分以内 \\
\quad $\square$ & Less than an hour / 1時間以内 \\
\quad $\square$ & More than an hour / 1時間以上 \\
\end{tabular}
\vspace{.1in}

\radioquestion{12}{Do you think the system is interesting?}{このシステムは面白かったですか？}{Extremely insteresting}{Extremely useless}{とても面白かった}{全然面白くなかった}

\radioquestion{13}{Did you feel frustrated or bored at any point when using the system?}{システムを作成する中で、プレッシャーに感じたりつまらないと思う点がありましたか？}{Felt engaged}{Felt bored/frustrated}{全然感じなかった}{感じる点が多かった}

\radioquestion{14}{Are you satisfied with the capabilities of the system?}{このシステムに満足しましたか？}{Very much satisfied}{Completely dissatisfied}{とても満足した}{全然満足できなかった}

\radioquestion{15}{Will you buy such a system if you have the robot and sensors with you?}{もしロボットやセンサーがあれば、このシステムを買いたいと思いますか？}{Very much satisfied}{Completely dissatisfied}{買いたいと思う}{全然買いたいと思わない}

\radioquestion{16}{How would you rate the overall system?}{あなたのこのシステムに対する評価はどのくらいですか？}{Very good}{Very poor}{とても高い}{とても低い}

\vspace{.05in}
%\hrule 
\begin{tabular}{rl}
\textbf{17} & \textbf{What are the other functions you would like to have in such a system?}\\
{} & \textbf{追加したほうがよい機能はありましたか？}\\
\end{tabular}

\begin{tabular}{c}
\quad \hdashrule{14cm}{2pt}{2pt} \\
\quad \hdashrule{14cm}{2pt}{2pt} \\
\quad \hdashrule{14cm}{2pt}{2pt} \\
\end{tabular}
\vspace{.1in}

\vspace{.05in}
%\hrule 
\begin{tabular}{rl}
\textbf{18} & \textbf{What are the things you would like us to improve in the system?}\\
{} & \textbf{改善したほうがよい点はありましたか？}\\
\end{tabular}

\begin{tabular}{c}
\quad \hdashrule{14cm}{2pt}{2pt} \\
\quad \hdashrule{14cm}{2pt}{2pt} \\
\quad \hdashrule{14cm}{2pt}{2pt} \\
\end{tabular}
\vspace{.1in}

\vspace{.05in}
%\hrule 
\begin{tabular}{rl}
\textbf{19} & \textbf{You general comments about the system}\\
{} & \textbf{その他、なにかコメントはありますか？}\\
\end{tabular}

\begin{tabular}{c}
\quad \hdashrule{14cm}{2pt}{2pt} \\
\quad \hdashrule{14cm}{2pt}{2pt} \\
\quad \hdashrule{14cm}{2pt}{2pt} \\
\end{tabular}
\vspace{.1in}

\section*{Multi-robot programming/複数のロボットに対するプログラムについて}
\vspace{.05in}
%\hrule 
\begin{tabular}{rl}
\textbf{20} & \textbf{Did you use the system to program more than one robot?}\\
{} & \textbf{複数のロボットに対するプログラムを作成しましたか？}\\
\end{tabular}

\begin{tabular}{rl}
\quad $\square$ & Yes / はい \\
\quad $\square$ & No /  いいえ \\
\end{tabular}
\vspace{.1in}

\radioquestion{21}{Was it easy to program multiple robots with the system?}{複数のロボットに対するプログラムは簡単でしたか？}{Very easy}{Very difficult}{とても簡単だった}{とても難しかった}

\vspace{.05in}
%\hrule 
\begin{tabular}{rl}
\textbf{22} & \textbf{Did you try to program multiple robots to operate in parallel?}\\
{} & \textbf{複数のロボットを同時に制御しましたか？}\\
\end{tabular}

\begin{tabular}{rl}
\quad $\square$ & Yes / はい \\
\quad $\square$ & No /  いいえ \\
\end{tabular}
\vspace{.1in}

\radioquestion{23}{Was it easy to program multiple robots to operate in parallel?}{複数のロボットを同時に制御することは簡単でしたか？}{Very easy}{Very difficult}{とても簡単だった}{とても難しかった}

\radioquestion{24}{Do you think ability to program multiple robots is needed?}{複数のロボットに対する機能は必要だと感じましたか？}{Strongly agree}{Disagree}{とてもそう思う}{そうは思わない}

\section*{Background/あなたについて}
\vspace{.05in}
%\hrule 
\begin{tabular}{rl}
\textbf{25} & \textbf{How old are you?}\\
{} & \textbf{あなたの年齢は？}\\
\end{tabular}

\begin{tabular}{c}
\quad \hdashrule{4cm}{2pt}{2pt} \\
\end{tabular}
\vspace{.1in}

\vspace{.05in}
%\hrule 
\begin{tabular}{rl}
\textbf{26} & \textbf{Gender}\\
{} & \textbf{あなたの性別は？}\\
\end{tabular}

\begin{tabular}{rl}
\quad $\square$ & Female / 女性 \\
\quad $\square$ & Male /  男性 \\
\end{tabular}
\vspace{.1in}

\vspace{.05in}
%\hrule 
\begin{tabular}{rl}
\textbf{27} & \textbf{What do you do?}\\
{} & \textbf{あなたはなにをされていますか？}\\
\end{tabular}

\begin{tabular}{rl}
\quad $\square$ & High school / 高校生 \\
\quad $\square$ & University /  大学生 \\
\quad $\square$ & Employed /  社会人 \\
\quad $\square$ & Others /  その他 \quad \hdashrule{4cm}{2pt}{2pt} \\
\end{tabular}
\vspace{.1in}

\radioquestion{28}{Have you interacted with real robot before?}{今までに実際のロボットを使ったことがありますか？}{not at all}{a lot}{全然ない}{よく使っている}

\radioquestion{29}{Do you have an experience in programming?}{プログラミングの経験はありますか？}{not at all}{a lot}{全然ない}{よく使っている}

\radioquestion{30}{Rate your programming skill}{あなたのプログラミングスキルはどのくらいですか？}{unskilled}{expert}{とても低い}{とても高い}

\vspace{.05in}
%\hrule 
\begin{tabular}{rl}
\textbf{31} & \textbf{Do you have background in robotics?}\\
{} & \textbf{ロボット工学に対する経験はありますか？}\\
\end{tabular}

\begin{tabular}{rl}
\quad $\square$ & Yes / はい \\
\quad $\square$ & No /  いいえ \\
\end{tabular}
\vspace{.1in}

\vspace{.05in}
%\hrule 
\begin{tabular}{rl}
\textbf{32} & \textbf{Have you programmed a robot before?}\\
{} & \textbf{いままでにロボットに対するプログラムを作成したことがありますか？}\\
\end{tabular}

\begin{tabular}{rl}
\quad $\square$ & Yes / はい \\
\quad $\square$ & No /  いいえ \\
\end{tabular}
\vspace{.1in}
\end{Form}